Methodology for Assessing the State of the Practice for Domain X

### 2020-09-02 StateOfPractice/Methodology/Methodology.tex
updated 'AHP' in Methodology document

\section{Analytic Hierarchy Process} \label{SecAHP}

Describe process. Domain experts review. Outline the tool we used. The README file of the tool can be found \href{run:../AHP2020/LBM/README.txt}{here}.

>>>>

\section{Analytic Hierarchy Process} \label{SecAHP}
The Analytical Hierarchy Process (AHP) is a decision making technique that can be used when comparing multiple options by multiple criteria. In our work AHP is used for comparing and ranking the software packages of a domain using the quality scores that are gathered in the \href{run:Combined_MeasurementTemplate_EmpiricalMeasures.xlsx}{Measurement Template}. AHP performs a pairwise analysis between each of the quality options using a matrix which is then used to generate an overall score for each software package for the given criteria. More information on AHP is available in \cite{SmithEtAl2016} We have developed a tool for conducting this process. The tool includes an AHP JAR script and a sensitivity analysis JAR script that is used to ensure that the software package rankings are appropriate with respect to the uncertainty of the quality scores.The README file of the tool is found \href{run:../AHP2020/LBM/README.txt}{here}. This file outlines the requirements for, and configuration and usage of the JAR scripts. The JAR scripts, source code, and required libraries are located in the same folder as the README file.
